### 2019-01-08 fe_px_paper/fe_body_text.tex
Updated abstract and conclusion. Sending to co-authors for revision

These results have several notable features.
The various \ce{^{nat}Fe}, \ce{^{nat}Cu}, and \ce{^{nat}Ti}(p,x) cross sections measured here are in excellent agreement with the body of measurements in the literature,  but have been measured nearly exclusively with the highest precision to date.
While (p,x) reactions below 70\,MeV on these elements are well-characterized overall, measurements of several reaction channels are somewhat sparse in comparison.
Indeed, fewer than four existing measurements have been performed for the \ce{^{nat}Fe}(p,x)\ce{^{48}Cr},\ce{^{52}Fe}, \ce{^{nat}Cu}(p,x)\ce{^{60}Cu},\ce{^{61}Co}, and \ce{^{nat}Ti}(p,x)\ce{^{44}Sc}
% Similarly, the various \ce{^{nat}Nb}(p,x) cross sections measured here are in excellent agreement with literature data, which is far more sparse in the 40--90\,MeV region than for \ce{^{nat}Cu}(p,x) ---  fewer than three existing measurements have been performed for the majority of the 
reactions presented here.
% Indeed,  the \ce{^{nat}Nb}(p,x)\ce{^{83}Sr}, \ce{^{nat}Nb}(p,x)\ce{^{85}Y}, \ce{^{nat}Nb}(p,x)\ce{^{89}Nb}, \ce{^{nat}Nb}(p,x)\ce{^{90}Mo}, \ce{^{nat}Nb}(p,x)\ce{^{91m}Nb}, and \ce{^{nat}Nb}(p,x)\ce{^{98m}Mo} reactions each possess no more than a total of three data points in this energy region.
% Not only do the \ce{^{nat}Nb}(p,x) measurements in this work fill in the sparse data in this energy region, but they have been measured with the highest precision relative to existing literature data.

@@

We present here a set of measurements of 34 cross sections for the \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and  \ce{^{nat}Ti}(p,x) reactions up to 55\,MeV, as well as  independent measurements of three isomer branching ratios.
Nearly all cross sections have been reported with higher precision than previous measurements.
\textred{We report the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90\,MeV region.}
% We advise that future activation experiments avoid the use of silicone-based adhesives, particularly in conjunction with aluminum monitor foils, to avoid reporting an enhanced fluence due to \ce{^{22,24}Na} contamination.
We also use these measurements to illustrate the deficiencies in the current state of  reaction modeling up to 55\,Me for  \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and  \ce{^{nat}Ti}(p,x) reactions.
Finally, this work provides another example of the usefulness of the recently-described variance minimization techniques for reducing energy uncertainties in stacked target charged particle irradiation experiments.

% We present here a set of 38 measurements of cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90 MeV, as well as five independent measurements of isomer branching ratios.
% Nearly all cross sections have been reported with higher precision than previous measurements.
% We report the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90\,MeV region.
% We advise that future activation experiments avoid the use of silicone-based adhesives, particularly in conjunction with aluminum monitor foils, to avoid reporting an enhanced fluence due to \ce{^{22,24}Na} contamination.
% We also use these measurements to illustrate the deficiencies in the current state of  reaction modeling for 40--90\,MeV \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
% Finally, this work provides another example of the usefulness of the recently-described variance minimization techniques for reducing energy uncertainties in stacked target charged particle irradiation experiments.

>>>>

These results have several notable features.
The various \ce{^{nat}Fe}, \ce{^{nat}Cu}, and \ce{^{nat}Ti}(p,x) cross sections measured here are in excellent agreement with the body of measurements in the literature,  but have been measured nearly exclusively with the highest precision to date.
While (p,x) reactions below 70\,MeV on these elements are well-characterized overall, measurements of several reaction channels are somewhat sparse in comparison.
Indeed, fewer than four existing measurements have been performed for the \ce{^{nat}Fe}(p,x)\ce{^{48}Cr},\ce{^{52}Fe}, \ce{^{nat}Cu}(p,x)\ce{^{60}Cu},\ce{^{61}Co}, and \ce{^{nat}Ti}(p,x)\ce{^{44}Sc}
% Similarly, the various \ce{^{nat}Nb}(p,x) cross sections measured here are in excellent agreement with literature data, which is far more sparse in the 40--90\,MeV region than for \ce{^{nat}Cu}(p,x) ---  fewer than three existing measurements have been performed for the majority of the 
reactions presented here.
% Indeed,  the \ce{^{nat}Nb}(p,x)\ce{^{83}Sr}, \ce{^{nat}Nb}(p,x)\ce{^{85}Y}, \ce{^{nat}Nb}(p,x)\ce{^{89}Nb}, \ce{^{nat}Nb}(p,x)\ce{^{90}Mo}, \ce{^{nat}Nb}(p,x)\ce{^{91m}Nb}, and \ce{^{nat}Nb}(p,x)\ce{^{98m}Mo} reactions each possess no more than a total of three data points in this energy region.
% Not only do the \ce{^{nat}Nb}(p,x) measurements in this work fill in the sparse data in this energy region, but they have been measured with the highest precision relative to existing literature data.
Additionally, \ce{^{22,24}Na} activity is seen in all foils, consistent with proton activation of the trace  silicon in the Kapton tape used for foil encapsulation, as described in our previous work \cite{Voyles2018a}.
No cross sections are reported due to the significant uncertainty in characterizing the layer of silicone adhesive, but this serves as another example of how the use of silicone-based adhesives may systematically enhance the apparent fluence when using the \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} monitor reactions.

@@

We present here a set of measurements of 34 cross sections for the \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and  \ce{^{nat}Ti}(p,x) reactions up to 55\,MeV, as well as  independent measurements of three isomer branching ratios.
Nearly all cross sections have been reported with higher precision than previous measurements.
We report the first measurements  for $\leq$70\,MeV protons  of the  \ce{^{nat}Fe}(p,x)\ce{^{49}Cr}, \ce{^{nat}Fe}(p,x)\ce{^{51}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{52m}Mn},  \ce{^{nat}Fe}(p,x)\ce{^{56}Mn}, and \ce{^{nat}Fe}(p,x)\ce{^{58m}Co} reactions, as well as the first measurement of the independent cross sections for    \ce{^{nat}Fe}(p,x)\ce{^{51}Cr}, \ce{^{nat}Fe}(p,x)\ce{^{52g}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{58g}Co}, and the \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$) and \ce{^{58\text{m}}Co} ($5^+$) / \ce{^{58\text{g}}Co}  ($2^+$)  isomer branching ratios via \ce{^{nat}Fe}(p,x).
% We advise that future activation experiments avoid the use of silicone-based adhesives, particularly in conjunction with aluminum monitor foils, to avoid reporting an enhanced fluence due to \ce{^{22,24}Na} contamination.
We also use these measurements to illustrate the deficiencies in the current state of  reaction modeling up to 55\,Me for  \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and  \ce{^{nat}Ti}(p,x) reactions.
Finally, this work provides another example of the usefulness of the recently-described variance minimization techniques for reducing energy uncertainties in stacked target charged particle irradiation experiments.
